nmds-plots

### 2023-02-13 workflow/notebooks/nmds-plots.Rmd
preliminary plot of pcoa

xx = ggplot(data.scores, aes(x = NMDS1, y = NMDS2)) + 
    geom_point(data=data.scores)

@@

>>>>

xx = ggplot(data.scores, aes(x = NMDS1, y = NMDS2)) + 
    geom_point(data=data.scores)+
  theme(axis.text.y = element_text(colour = "black", size = 12, face = "bold"), 
    axis.text.x = element_text(colour = "black", face = "bold", size = 12), 
    legend.text = element_text(size = 12, face ="bold", colour ="black"), 
    legend.position = "right", axis.title.y = element_text(face = "bold", size = 14), 
    axis.title.x = element_text(face = "bold", size = 14, colour = "black"), 
    legend.title = element_text(size = 14, colour = "black", face = "bold"), 
    panel.background = element_blank(), panel.border = element_rect(colour = "black", fill = NA, size = 1.2),
    legend.key=element_blank()) + 
    labs(x = "NMDS1", colour = "Time", y = "NMDS2", shape = "Type")  + 
    scale_colour_manual(values = c("#009E73", "#E69F00"))

@@

```{r pcoa, include=FALSE}
pcoa_data <- read_tsv("/Users/megan/Desktop/schloss-lab/adverseCDI/data/mothur/cdi.opti_mcc.braycurtis.0.03.lt.ave.pcoa.axes")
modified <- pcoa_data[,2:ncol(pcoa_data)]
ordiplot (modified)
# pcoa.plot(pcoa_data, is.OTU=TRUE, meta, factors, rank,  stand.method = NULL, dist.method = "morisita",  sample.labels = TRUE, top = 20, ellipse = FALSE, main = NULL, file = NULL, ext = NULL, height = 8, width = 10, ggplot2 = TRUE, bw = FALSE)
```
